Effects of masked prime duration in an online lexical decision task

### 2021-03-12 Manuscript.Rmd
brms analyses

```{r load_exp1_data, message=FALSE, echo=FALSE}
library(tidyverse)
library(sp)
library(rworldmap)

@@

e1_actual_participants <- filter(e1_all_participants, PROLIFIC_PID %in% e1$participant & `What is your age?` != 99)

@@

other_participants_nr <- filter(e1_actual_participants, `What is your gender (optional)?` == "Other") %>% nrow

NA_participants_nr <- filter(e1_actual_participants, `What is your gender (optional)?` == "Other") %>% nrow
```

@@

We collected data from `r e1_actual_participants$PROLIFIC_PID %>% unique %>% length` participants aged from `r participant_ages %>% min` to `r participant_ages %>% max` (mean age: `r participant_ages %>% mean %>% round(2)`) recruited through Prolific [www.prolific.co, -@prolific2021]. Of the participants, The experiment was only be shown to participants who have indicated that English is their first language in the Prolific screening questions. They were paid £1.25 for their participation (corresponding to £5/hour). Participants indicated that English was their first language before starting the experiment.

### Material

@@

@@

\newpage

>>>>

```{r load_exp1_data, message=FALSE, echo=FALSE}
library(xfun)
library(tidyverse)
library(sp)
library(rworldmap)

@@

# only consider participants who have actually participated in the whole experiment
# also don't consider participants whose age is 99 (used for testing)
# one participant is duplicate. Remove the first occurrence (likely incompatible device)

e1_actual_participants <- filter(e1_all_participants, PROLIFIC_PID %in% e1$participant & `What is your age?` != 99 & `Response ID` != "R_sU4qJ6UCe9jRKs9")

@@

# there aren't actually any of these, but will leave the code in just in calse
other_participants_nr <- filter(e1_actual_participants, `What is your gender (optional)?` == "Other") %>% nrow

NA_participants_nr <- filter(e1_actual_participants, is.na(`What is your gender (optional)?`)) %>% nrow

#coordinates(e1_actual_participants) <- c("Location Longitude","Location Latitude")

# from https://stackoverflow.com/questions/14334970/convert-latitude-and-longitude-coordinates-to-country-name-in-r

# The single argument to this function, points, is a data.frame in which:
#   - column 1 contains the longitude in degrees
#   - column 2 contains the latitude in degrees
coords2country = function(points)
{  
  countriesSP <- getMap(resolution='low')
  #countriesSP <- getMap(resolution='high') #you could use high res map from rworldxtra if you were concerned about detail

  # convert our list of points to a SpatialPoints object

  # pointsSP = SpatialPoints(points, proj4string=CRS(" +proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs +towgs84=0,0,0"))

  #setting CRS directly to that from rworldmap
  pointsSP = SpatialPoints(points, proj4string=CRS(proj4string(countriesSP)))

  # use 'over' to get indices of the Polygons object containing each point 
  indices = over(pointsSP, countriesSP)

  # return the ADMIN names of each country
  indices$ADMIN  
  #indices$ISO3 # returns the ISO3 code 
  #indices$continent   # returns the continent (6 continent model)
  #indices$REGION   # returns the continent (7 continent model)
}

participant_coords <- e1_actual_participants %>% select("Location Longitude", "Location Latitude")

e1_actual_participants$country <- coords2country(participant_coords)

e1_participant_countries <- table(e1_actual_participants$country %>% as.character) #make into a character vector since the original output is a factor with as many levels as there are countries
```

@@

We collected data from `r e1_actual_participants$PROLIFIC_PID %>% unique %>% length` participants aged from `r participant_ages %>% min` to `r participant_ages %>% max` (mean age: `r participant_ages %>% mean %>% round(2)`) recruited through Prolific [www.prolific.co, -@prolific2021]. Of the participants, `r male_participants_nr` identified as male and `r female_participants_nr` identified as female. The experiment was only shown to participants who indicated that English was their first language in the Prolific screening questions. Based on their IP addresses, `r e1_participant_countries["United Kingdom"] %>% ifelse(. < 11, numbers_to_words(.), .)` participants were based in the UK, `r e1_participant_countries["United States of America"] %>% ifelse(. < 11, numbers_to_words(.), .)` were based in the US, `r e1_participant_countries["Canada"] %>% ifelse(. < 11, numbers_to_words(.), .)` participants were based in Canada, and `r e1_participant_countries["Ireland"] %>% ifelse(. < 11, numbers_to_words(.), .)` participants were based in Ireland. Two participants could not be localized in this way. Participants who completed the experiment were paid £1.25 for their participation (corresponding to £5/hour). All participants were naïve to the purpose of the experiment.

### Materials

@@

Participants were able to sign up for the experiment on the Prolific website. On signing up, they were redirected to the participant agreement form on the Qualtrics online survey development environment [@qualtrics2020]. After indicating their agreement to participate, participants were forwarded to Pavlovia [@pavlovia2020], where the actual PsychoJS experiment was hosted. After completing the experiment, participants were redirected to a debriefing form on Qualtrics and from there back to Prolific in order to receive their participation payment.

@@

```{=html}
<script src="https://hypothes.is/embed.js" async></script>
```
\newpage

### 2021-03-12 Manuscript.tex
brms analyses

\textless\textless\textless\textless\textless\textless\textless{} HEAD:Manuscript.Rmd
\# Experiment 1

@@

\begin{verbatim}
## Warning: package 'sp' was built under R version 4.0.4
\end{verbatim}

\begin{verbatim}
## Warning: package 'rworldmap' was built under R version 4.0.4
\end{verbatim}

@@

We collected data from 77 participants aged from 18 to 71 (mean age: 31.08) recruited through Prolific (www.prolific.co, 2021). Of the participants, 41 identified as male, 37 identified as female, 0 identified as other, and 0 declined to identify their gender. The experiment was only shown to participants who indicated that English was their first language in the Prolific screening questions. Participants who completed the experiment were paid £1.25 for their participation (corresponding to £5/hour). All participants were naïve to the purpose of the experiment.

\hypertarget{material}{%
\subsubsection{Material}\label{material}}

@@

We used R {[}Version 4.0.3; R Core Team (2020){]} and the R-package \emph{papaja} {[}Version 0.1.0.9942; Aust and Barth (2020){]} for all our analyses.

@@

@@

@@

@@

@@

>>>>

\hypertarget{experiment-1}{%
\section{Experiment 1}\label{experiment-1}}

@@

@@

We collected data from 77 participants aged from 18 to 71 (mean age: 31.14) recruited through Prolific (www.prolific.co, 2021). Of the participants, 41 identified as male and 36 identified as female. The experiment was only shown to participants who indicated that English was their first language in the Prolific screening questions. Based on their IP addresses, 47 participants were based in the UK, 23 were based in the US, three participants were based in Canada, and two participants were based in Ireland. Two participants could not be localized in this way. Participants who completed the experiment were paid £1.25 for their participation (corresponding to £5/hour). All participants were naïve to the purpose of the experiment.

\hypertarget{materials}{%
\subsubsection{Materials}\label{materials}}

@@

We used R {[}Version 4.0.4; R Core Team (2020){]} and the R-packages \emph{dplyr} {[}Version 1.0.5; Wickham, François, Henry, and Müller (2021){]}, \emph{forcats} {[}Version 0.5.1; Wickham (2021a){]}, \emph{ggplot2} {[}Version 3.3.3; Wickham (2016){]}, \emph{papaja} {[}Version 0.1.0.9942; Aust and Barth (2020){]}, \emph{purrr} {[}Version 0.3.4; Henry and Wickham (2020){]}, \emph{readr} {[}Version 1.4.0; Wickham and Hester (2020){]}, \emph{rworldmap} {[}Version 1.3.6; South (2011){]}, \emph{sp} {[}Version 1.4.5; Pebesma and Bivand (2005){]}, \emph{stringr} {[}Version 1.4.0; Wickham (2019){]}, \emph{tibble} {[}Version 3.1.0; Müller and Wickham (2021){]}, \emph{tidyr} {[}Version 1.1.3; Wickham (2021b){]}, and \emph{tidyverse} {[}Version 1.3.0; Wickham et al. (2019){]} for all our analyses.

@@

\leavevmode\hypertarget{ref-R-purrr}{}%
Henry, L., \& Wickham, H. (2020). \emph{Purrr: Functional programming tools}. Retrieved from \url{https://CRAN.R-project.org/package=purrr}

@@

\leavevmode\hypertarget{ref-R-tibble}{}%
Müller, K., \& Wickham, H. (2021). \emph{Tibble: Simple data frames}. Retrieved from \url{https://CRAN.R-project.org/package=tibble}

@@

\leavevmode\hypertarget{ref-R-sp}{}%
Pebesma, E. J., \& Bivand, R. S. (2005). Classes and methods for spatial data in {R}. \emph{R News}, \emph{5}(2), 9--13. Retrieved from \url{https://CRAN.R-project.org/doc/Rnews/}

@@

\leavevmode\hypertarget{ref-R-rworldmap}{}%
South, A. (2011). Rworldmap: A new r package for mapping global data. \emph{The R Journal}, \emph{3}(1), 35--43. Retrieved from \url{http://journal.r-project.org/archive/2011-1/RJournal_2011-1_South.pdf}

@@

\leavevmode\hypertarget{ref-R-ggplot2}{}%
Wickham, H. (2016). \emph{ggplot2: Elegant graphics for data analysis}. Springer-Verlag New York. Retrieved from \url{https://ggplot2.tidyverse.org}

\leavevmode\hypertarget{ref-R-stringr}{}%
Wickham, H. (2019). \emph{Stringr: Simple, consistent wrappers for common string operations}. Retrieved from \url{https://CRAN.R-project.org/package=stringr}

\leavevmode\hypertarget{ref-R-forcats}{}%
Wickham, H. (2021a). \emph{Forcats: Tools for working with categorical variables (factors)}. Retrieved from \url{https://CRAN.R-project.org/package=forcats}

\leavevmode\hypertarget{ref-R-tidyr}{}%
Wickham, H. (2021b). \emph{Tidyr: Tidy messy data}. Retrieved from \url{https://CRAN.R-project.org/package=tidyr}

\leavevmode\hypertarget{ref-R-tidyverse}{}%
Wickham, H., Averick, M., Bryan, J., Chang, W., McGowan, L. D., François, R., \ldots{} Yutani, H. (2019). Welcome to the {tidyverse}. \emph{Journal of Open Source Software}, \emph{4}(43), 1686. \url{https://doi.org/10.21105/joss.01686}

\leavevmode\hypertarget{ref-R-dplyr}{}%
Wickham, H., François, R., Henry, L., \& Müller, K. (2021). \emph{Dplyr: A grammar of data manipulation}. Retrieved from \url{https://CRAN.R-project.org/package=dplyr}

\leavevmode\hypertarget{ref-R-readr}{}%
Wickham, H., \& Hester, J. (2020). \emph{Readr: Read rectangular text data}. Retrieved from \url{https://CRAN.R-project.org/package=readr}
